---
title: "UsedCar"
output:
  word_document: default
  pdf_document: default
  html_document: default
---
(1) Load the dataframe into R:

```{r}
Cars.Data.Smaller<-read.csv("What path you have your csv.file stored")
str(Cars.Data.Smaller)
```

(2)Create a new dataframe called "cars.price" for the question: 
```{r}
cars.price<-Cars.Data.Smaller[, c("mileage", "year", "price", "horsepower", "daysonmarket")]
str(cars.price)
```

(3)Check each of the attributes for NAs.

```{r}
any(is.na(cars.price$mileage))# Yes NA values to mileage 
length(cars.price$mileage[is.na(cars.price$mileage)]) #number of NAs in owner_count is 282.
any(is.na(cars.price$horsepower)) #Yes NA values to horsepower.
length(cars.price$horsepower[is.na(cars.price$horsepower)]) #number of NAs in horsepower is 209.
any(is.na(cars.price$daysonmarket))#No NA values to daysonmarket
any(is.na(cars.price$year))# No NA values in year.
any(is.na(cars.price$price))# No NA values in price. 
```

(4) Handle NA values in the dataset
```{r}
library(imputeTS)
```

Handle NAs in mileage. Since the missing value is only approximately 200 cases, I chose to just go ahead and replace the NA with mean value. 
```{r}
cars.price$mileage<-na_interpolation(cars.price$mileage)
summary(cars.price$mileage)
```
Remove NAs in horsepower
```{r}
cars.price$horsepower<-na_interpolation(cars.price$horsepower)
summary(cars.price$horsepower)
```

```{r}
str(cars.price)
```

Here are my business questions:  How does the number of previous owners, mileage, year, cylinders, and car makes predict the price of the used cars?

4. Visualize the data first. 
```{r}
library(ggplot2)
```
Creating best fit lines with the ggplot for four variables. 
```{r}
#color choices for R base plot using brewer.pal(n, name)
library(RColorBrewer)
brewer.pal(n=9, name="RdBu")
#4 colors for each color palette 
```
```{r}
library(ggpubr) #library for ggarrange()
```

```{r}
#visualization of the car inventory by car price 
ggplot(cars.price, aes(x=price))+geom_histogram(color="black", fill="#a1e9f0")+
  ggtitle("Distribution of Car Price in Inventory")
```


```{r}
plot.horsepower<-ggplot(cars.price, aes(x=horsepower, y=price))+geom_point()+stat_smooth(method="lm", col="#D6604D")+ggtitle("Price~Horsepower")
plot.year<-ggplot(cars.price, aes(x=year, y=price))+geom_point()+stat_smooth(method="lm", col="#F4A582")+ggtitle("Price~Year")
plot.mileage<-ggplot(cars.price, aes(x=mileage, y=price))+geom_point()+stat_smooth(method="lm", col="#92C5DE")+ggtitle("Price~Mileage") #figure out why the abline is below zero 
plot.daysonmarket<-ggplot(cars.price, aes(x=daysonmarket, y=price))+geom_point()+stat_smooth(method="lm", col="#2166AC")+ggtitle("Price~Daysonmarket")
plots <- ggarrange(plot.horsepower,plot.year,plot.mileage, plot.daysonmarket,
                    ncol = 2, nrow = 2) #combine ggplots
plots
# http://www.sthda.com/english/articles/32-r-graphics-essentials/126-combine-multiple-ggplots-in-one-graph/
```


5. Linear models for the variables, # preownership, mileage, year, horsepower, daysonmarket.

```{r}
mileagePred<-lm(price~mileage, data=cars.price)
summary(mileagePred)
```


```{r}
yearPred<-lm(price~year, data=cars.price)
summary(yearPred)
```

```{r}
horsepowerPred<-lm(price~horsepower, data=cars.price)
summary(horsepowerPred)
```

```{r}
daysPred<-lm(price~daysonmarket, data=cars.price)
summary(daysPred)
```

https://rpubs.com/justingee193/rprof_lm 

Load the needed libraries
```{r}
library(caret)
```

```{r}
#new dataset without daysonmarket since it does not have a great impact on the car price
cars<-cars.price[, -5]
str(cars)
```


```{r}
#Split the data into train v.s. test data
set.seed(111)
train_list<-createDataPartition(y=cars$price, p=0.66, list=FALSE)
train<-cars[train_list,]
test<-cars[-train_list,]
dim(train)
dim(test)
```

```{r}
#building the model with train dataset. 
model2<-train(price~., data=train,
                 method = "lm", 
                 preProcess=c("scale", "center"),
                 trControl=trainControl(method="none")) 
summary(model2)
#Apply model for prediction
model.train<-predict(model2, train)
model.test<-predict(model2, test) #apply model to make prediction on test dataset 
#Model performance by visualization 
plot(train$price, model.train, col = "blue", xlab="price", ylab="predicted",sub = "Model performance for train v.s. test")
points(test$price, model.test, col = "red") #overlay test set over train set. 
```

```{r}
#Coefficient for train v.s. test: 
r.train<-cor(train$price, model.train)
r.test<-cor(test$price, model.test)
r2.train<-r.train^2
r2.test<-r.test^2
r2.train
r2.test
#The code used in here is inspired by: https://www.youtube.com/watch?v=el8xP38SWdk&ab_channel=DataProfessor 
```
```{r}
library(tidyverse)
```

```{r}
#Predict with a given car:
year<-c(2008, 2013, 2017, 2020)
horsepower<-c(186, 254, 310, 285)
mileage<-c(91733, 81807, 42942, 14252)
test<-data.frame(year, horsepower, mileage)
pricepred<- predict(model2,newdata=test)
pricepred
test.price<-data.frame(horsepower, mileage, year,pricepred)
view(test.price)
```




